Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-27 csf2/main.tex
more on four

The combination of \gls*{ms} and \gls*{scct} is the intersection of these properties, \gls*{msscct}.
However, \gls*{ms} uses a different trace model than \gls*{scct}, so intersecting them would trivially yield the empty set. 
To remedy this issue, let $\sim_{\ctsafe}$ be a cross-language trace relation whose definition can be sketched as follows:
\[
  \typerulenolabel{mscctrel:drop:tag}{}{\preevent[_{\mssafe}]\sim_{\ctsafe}\preevent[_{\mssafe}];\securitytag}
  \typerulenolabel{mscctrel:drop:crash}{}{\lightning\sim_{\ctsafe}\lightning}
\]
\[
  \typerulenolabel{mscctrel:drop:branch}{}{\emptyevent\sim_{\ctsafe}\ev{Branch n};\securitytag}
  \typerulenolabel{mscctrel:drop:binop}{}{\emptyevent\sim_{\ctsafe}\ev{Binop n};\securitytag}
\]

@@

\begin{definition}[\glsfirst*{ms} and \gls*{scct}]\label{def:trace:msscctdef}
  $
  \msscctsafe:=\sigma_{\sim_{msscct}}\left(\mssafe\right)\cap\scctsafe
  $
\end{definition}

@@

So far, the considered trace models do not take speculative execution into account. 
For this, extend the earlier trace model (see \Cref{subsec:scct:tracemodel}) so that the security tags ($\securitytag$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
Moreover, add base-events signaling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.

>>>>

The combination of \gls*{ms} and \gls*{scct} is the intersection of these properties, \gls*{msscct}.
However, \gls*{ms} uses a different trace model than \gls*{scct}, so intersecting them would trivially yield the empty set. 
To remedy this issue, let $\sim_{\ctsafe}$ be a cross-language trace relation whose definition can be sketched as follows:\MP{why just sketched?}
\[
  \typerulenolabel{mscctrel:drop:tag}{}{\preevent[_{\mssafe}]\sim_{\ctsafe}\preevent[_{\mssafe}];\securitytag}
  \typerulenolabel{mscctrel:drop:crash}{}{\lightning\sim_{\ctsafe}\lightning}
\]
\[
  \typerulenolabel{mscctrel:drop:branch}{}{\emptyevent\sim_{\ctsafe}\ev{Branch n};\securitytag}
  \typerulenolabel{mscctrel:drop:binop}{}{\emptyevent\sim_{\ctsafe}\ev{Binop n};\securitytag}
\]

@@

\begin{definition}[\gls*{ms} and \gls*{scct}]\label{def:trace:msscctdef}
  $
  \msscctsafe:=\sigma_{\sim_{mct}}\left(\mssafe\right)\cap\scctsafe
  $
\end{definition}

@@

So far, the considered trace models do not let us express speculative execution attacks such as Spectre~\cite{}\MP{cits}. 
For this, we extend the earlier trace model (see \Cref{subsec:scct:tracemodel}) so that the security tags ($\securitytag$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
Moreover, add base-events signaling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.
